---
title: "Bonferroni Function Development"
author: "Mike Seaman"
date: "2 April 2020"
output: html_notebook
---

This notebook is for the development of a function to construct Bonferroni
confidence interval when we have more than two conditions in our study.

This is the function, bonf_cis, that will construct Bonferroni confidence 
intervals.

Required arguments:

A matrix with the units in rows and the conditions in columns

A matrix with each row containing the number of conditions to compare in the
two columns

A numeric with the level of confidence

Returns:

A matrix with each row containing the two conditions being compared and the
lower and upper bounds for a confidence interval for the difference in means

```{r}
bonf_cis <- function(my_data, my_comp, conf.level) {

  
    
  return(my_cis)
}
```


This next code chunk is for testing the bonf_cis function using the hsb2 data.

```{r}

hsb2 <- read.csv("hsb2.csv")

ses_math <- cbind(hsb2$ses, hsb2$math)

comparisons <- matrix(c(1, 3,
                        2, 3),
                      ncol = 2,
                      byrow = TRUE)

bonf_cis(ses_math, comparisons, .95)

```


